Turbulence and Particle Acceleration in Giant Radio Haloes: the Origin of Seed Electrons

### 2016-06-24 paper.tex
additions as a result of a skype chat with Peng

We adopt a Kraichnan spectrum ($s=3/2$) for the fast modes, as seen in simulations \citep{cho03}. This can also be written as: 
\begin{equation}
  \label{eq:Wk}
  \mathcal{W}(k) =
\sqrt{2/7\,I_L\,\rho\,\langle \Vph \rangle}\,k^{-3/2},
\end{equation}
where $I_L$ is the volumetric injection rate of turbulence at scale $L$ (which is assumed to be constant), $\varv_{\rm ph}\approx c_{\rm s}$ is the phase speed of waves. \cp{Since the Kraichnan spectrum is critical in what follows, it is worthwhile taking a moment to recount the origin of the spectral slope $s$ and the cascade rate. In the magnetically dominated regime, two counterpropagating wave packets of scale $l$ interact on an Alfv{\'e}n time $\tau_{\rm A}=l/\varv_{\rm A}$, rather than the eddy turnover time $\tau_{\rm edd} = l/\varv_{\rm l}$. 
Since $\tau_{\rm A} \ll \tau_{\rm edd}$, each interaction results in a small velocity change $\delta \varv_{\rm l} \sim \varv_{\rm l} (\tau_{\rm A}/\tau_{\rm edd})$. If these changes behave like a random walk, the cascade time $\tau_{\rm l}$ it takes for an eddy to become non-linear ($\Delta \varv \sim \varv_{\rm l})$ and cascades to smaller scales occurs with a characteristic velocity $\varv_{\rm l} \sim \delta \varv_{\rm l} (\tau_{\rm l}/\tau_{\rm A})^{1/2} \sim \varv_{\rm l} \tau_{\rm A}/\tau_{\rm edd} (\tau_{\rm l}/\tau_{\rm A})^{1/2}$, which we can solve to obtain the cascade time: 
\begin{equation}
  \label{eqn:tau_l}
\tau_{\rm l} \sim \left(\frac{\tau_{\rm edd}}{\tau_{\rm A}}\right)^{2} \tau_{\rm A} \sim \frac{l \varv_{\rm A}}{\varv_{\rm l}^{2}} 
\end{equation}
where we have implicitly assumed isotropy. This implies a dissipation rate $\epsilon \sim \varv_{\rm l}^{2}/\tau_{\rm l} \sim \varv_{\rm l}^{4}/(l \varv_{\rm A})$, or $\varv_{\rm l} \sim (\epsilon l \varv_{A})^{1/4}$. Thus, since $k E(k)\sim \varv_{\rm l}^{2}$, this gives a kinetic energy spectrum: 
\begin{equation}
E(k) \sim (\epsilon \varv_{\rm A})^{1/2} k^{-3/2}.
\end{equation}}

It is important to realise that this Kraichnan scaling only applies at small scales, where turbulence is magneto-hydrodynamical. At large scales, turbulent motions are subsonic (${\mathcal M}_{\rm s} \sim 0.2-0.5$) but super-Alfv{\'e}nic (${\mathcal M}_{\rm A} \sim 5$). Thus, except in the case where motions are transsonic and weak shocks become important, motions are fundamentally hydrodynamic and turbulence follows a Kolmogorov ($s=5/3$) spectrum. However, while the turbulent energy density $\eps_{\rm turb} \propto l^{2/3}$ decreases at small scales, the magnetic energy density is scale-independent. Thus, at some scale $l_{\rm A} \sim l_L {\mathcal M}_{\rm A}^{-3}$, where $\eps_{\rm turb} \sim \eps_{B}$, the magnetic field becomes dynamically important, and turbulence transitions to the MHD regime. The cutoff scale in equation (\ref{eqn:Wk}) can be computed by setting the turbulent cascade rate for fast modes to the transit time damping rate on thermal electrons. This yields \citep{brunetti07,miniati15}:
\begin{equation}
k_{\rm cut} \approx A k_{\rmn{outer}} \frac{\langle (\delta \varv_{\rmn{outer}})^{2}\rangle^{2}}{c_{\rm s}^{4}}
\label{eqn:k_c1} 
\end{equation}
where $A \approx 11 000$. \cp{If there is an unimpeded cascade from the injection to the cutoff scale, $k_{\rmn{outer}}=k_L$ and $\varv_{\rmn{outer}}=\varv_{\rmn{c}}$. However, in our case the hydrodynamic (Kolmogorov) cascade transitions to the MHD cascade at the Alfv{\'e}n scale so that $k_{\rmn{outer}}=k_{\rmn{A}}$ and $\varv_{\rmn{outer}}=\varv_{\rmn{A}}$ and hence, we get\footnote{\cp{Note that this differs from previous work which uses the wave number and compressible velocity at the outer scale $L$ for this estimate of $k_{\rm cut}$.}}
\begin{equation}
k_{\rm cut} \approx A k_{\rmn{A}} \beta^{-2}\,.
\label{eqn:k_c} 
\end{equation}
}
This gives $2\upi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
effective mean free path for CRs, unless plasma instabilities can
mediate interactions between turbulence and particles on smaller
scales \citep{brunetti11}, a possibility we discuss in \S\ref{sect:self-limiting}. Another possibility is that compressible modes dissipate in weak shocks, resulting in Burgers' turbulence $s=2$ \citep{kowal10,porter15,miniati15}. If Burgers turbulence dominates, then particle acceleration rates are too slow in the face of cooling processes to explain radio haloes \citep{miniati15}, and an alternative model for radio haloes is required.

@@

The important effects are best summarised in terms of the acceleration \cp{rate
  which is goverend by advection in momentum space:
\begin{equation}
  \tau_{\rm D}^{-1}\equiv \Gamma_{\rm D}\equiv
  \frac{\dot{p}}{p}=p^{-3}\frac{\partial}{\partial p}\left(p^2D_{pp}\right)
  =\frac{4 D_{pp}}{p^{2}}.
\end{equation}
In the last step we have used that $D_{pp}\propto p^2$ for the turbulent
reacceleration (equation \ref{eqn:Dpp}). Hence the acceleration time is independent of momentum.}
%\begin{equation}
%\tau_{\rm D}= \frac{p^{2}}{4 D_{pp}}
%\end{equation}
%which is momentum independent.
This should be compared against the lifetime of turbulence, $\tau_{\rm cl}$, and the cooling time $\tau_{\rm cool}$. In Table~\ref{tab:timescales}, we show both the thermal quantities and the
timescales for CR cooling and (re)acceleration for three different
spatial regions of the RH. The densities \citep{1992A&A...259L..31B} and temperatures \citep{2009ApJ...696.1886B,2001A&A...365L..67A} are derived from X-ray observations. To calculate synchrotron cooling times, we use $B$-fields derived from Faraday rotation measurements \citep{bonafede10}. To calculate the acceleration time, we need to assume an outer scale. We assume an injection scale $k_L=2\upi/\lambda_L$, where $\lambda_L = 100$ kpc, which were assumptions adopted in previous work \citep{2006MNRAS.366.1437S,brunetti07, brunetti11}. This length scale corresponds to an eddy turnover time on the outer scale of \cp{\sout{$\varv_L k_L^{-1} \sim 1.2$~Gyr} $2\upi\lambda_L\varv_L^{-1} \sim 1.2$~Gyr} if $\varv_L \sim 500 {\rm km \, s^{-1}}$, as is characteristic of a merger. Note that hydrodynamical simulations of clusters have sometimes found larger $\lambda_L$, in some cases comparable to the size of the cluster \citep{vazza11,miniati15}. This choice is degenerate with $X_{\rm tu}$; in \S\ref{sect:self-limiting} we argue that $k_{\rm A}$ is a more appropriate choice, but also find that when the decay time is appropriately scaled, we are relatively insensitive to the choice of $k_L$. We present $\tau_{\rm D}$ for 3 different models, which we discuss in the next section. The reacceleration timescale
$\tau_{\rm D}$ is similar between our three models, where the
difference comes from turbulent profile parametrized with
$\alpha_\rmn{tu}$. This implies that even small differences in the
turbulent profile could impact the seed CRs significantly. Finally, we adopt an duration of acceleration $\tau_{\rm cl} = 650$ Myr, in line with previous assumptions \citep{brunetti07}, roughly corresponding to the turbulent decay time. 
\begin{table}
  \caption{Thermal quantities and timescales for different spatial
    regions in a Coma like cluster.}
\begin{tabular}{l c  c c}
\hline
\hline
& & spatial regions & \\
 & $0.1\,\RH^{(2)}$ & $0.3\,\RH^{(2)}$ & $\RH^{(2)}$   \\
\hline
thermal quantities$^{(1)}$ & & & \\
$\rho$ [$10^{-27}$ g cm$^{-3}$] & 3.0 & 1.6 & 0.15 \\
$T$ [$10^{8}$ K] & 1.4 & 1.0 & 0.58 \\
\hline
timescales$^{(1)}$ & & & \\
$\tau_\rmn{D}$(\Mprimary)$^{(3)}$ [Gyr] & 0.45 & 0.44 & 0.39 \\
$\tau_\rmn{D}$(\Mstream)$^{(3)}$  [Gyr] & 0.50 & 0.47 & 0.34 \\
$\tau_\rmn{D}$(\Mflatturb)$^{(3)}$  [Gyr] & 0.69 & 0.56 & 0.27 \\
$\tau_\rmn{IC/sync}(P=10^4\,m_{\rmn{e}}c)^{(4)}$ [Gyr] & 0.11 & 0.15 & 0.22 \\
$\tau_\rmn{had}(P=100\,m_{\rmn{p}}c)^{(5)}$ [Gyr] & 2.4 & 4.5 & 47 \\
$\tau_\rmn{Coul}(P=\,m_{\rmn{e}}c)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.17 \\
\hline
\end{tabular}
\begin{quote}
 Notes: \\ 
 (1) Median quantities from our simulated post-merging cluster g72a derived 
 during last 300~Myrs in time. \\
 (2) Radius of the giant radio halo in Coma where $\RH\approx0.6\,R_{200}$.\\
 (3) Fermi-II reacceleration for both electrons and protons at all energies.\\
 (4) Inverse Compton and synchrotron cooling for electrons.\\
 (5) Catastrophic losses for protons.\\
 (6) Coulomb cooling for electrons (protons factor $m_{\rmn{e}}/m_{\rmn{p}}$ smaller).\\
 \label{tab:timescales}
  \end{quote}
\end{table}

@@

Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$, with velocity $\varv_{\rm A}$. The turbulent reacceleration time is: 
%\begin{equation}
%\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = C_{\rm D} A^{1/2} c k_{\rm A} \frac{\varv_{\rm A}^{2}}{c_{\rm S}^{2}}
%\label{eqn:tau_D} 
%\end{equation}
\cp{
  \begin{equation}
\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = \frac{C_{\rm D}}{A^{1/2}}\, \frac{c}{k_{\rm A}}\, \frac{c_{\rm s}^{2}}{\varv_{\rm A}^{4}}
\label{eqn:tau_D} 
\end{equation}
}
where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equation (\ref{eqn:k_c}). The turbulent decay time is given by the cascade time of fast modes \cp{at the Alfv\'en scale $k=k_{\rmn{A}}$} (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:cascade}): 
\begin{equation}
  \tau_{\rm decay} = \cp{\frac{\varv_{\rm ph}}{\varv_k^{2} k} = }
  \frac{c_{\rm s}}{\varv_{\rm A}^{2} k_{\rm A}^{}}\,.
\label{eqn:tau_decay} 
\end{equation}
This can be related to the eddy turnover time at the outer scale $\tau_{\rm edd}$ from $l_{\rm A} = L \mathcal{M}_{\rm A}^{-3}$ to: 
\begin{equation}
\tau_{\rm decay} =\frac{L}{\varv_{\rm c}} \left(\frac{c_{\rm s}}{\varv_{\rm c}} \right)^{2} \frac{\varv_{\rm A}}{c_{\rm s}} = 0.7 \, \tau_{\rm edd} \left(\frac{\tilde{X}_{\rm tu}}{0.2}\right)^{-1}  \left(\frac{\beta}{100} \right)^{-1/2}
\end{equation}
\cp{[I get 0.08 as prefactor mainly because of the $2\upi$ conversion from $k$ to $L$.]}
where we have used $\tilde{X}_{\rm tu} \approx (\varv_{\rm c}/c_{\rm s})^{2}$ and $c_{\rm s}/\varv_{\rm A} = \beta^{1/2}$. \cp{\sout{Thus $\tau_{\rm decay} \sim \tau_{\rm edd}$, but we prefer to use the expression for $\tau_{\rm edd}$, since it is more physically correct and leads to more revealing scalings. }}

From equations (\ref{eqn:tau_D}) and (\ref{eqn:tau_decay}), we obtain:
\begin{equation}
  \frac{\tau_{\rm cl}}{\tau_{\rm D}} \approx \frac{\tau_{\rm decay}}{\tau_{\rm D}}
  \cp{= \frac{A^{1/2}}{C_{\rmn{D}}}\,\frac{c_{\rm s}}{c}\,\beta^{-1}}
  = 0.1 \left( \frac{c_{\rm s}}{1500 \, {\rm km \, s^{-1}}} \right) \left( \frac{\beta}{50} \right)^{-1}\,. 
\label{eqn:ratios_TTD} 
\end{equation}
Remarkably, this expression is independent of properties of the turbulence such as $\varv_{\rm c}$, $L$, or $l_{\rm A}$, and depends only on properties of the plasma ($c_{\rm s},\beta$). Ultimately, this arises because the timescale on which a fast mode wave transfers energy due to wave particle interactions in second order Fermi acceleration, $\tau_{\rm p} \sim [\cp{4\,} k_{\rm p} c (\varv_{\rm c}/c)^{2} ]^{-1}$, is closely related to the timescale on which it cascades due to wave-wave interactions, $\tau_{\rm w} \sim c_{\rm s}/(k_{\rm w} \varv_{\rm c}^{2})$. This implies $\tau_{\rm w}/\tau_{\rm p} \sim \cp{4\,} (c_{\rm s}/c)(l_{\rm w}/l_{\rm p})$, where $l_{\rm w} \sim l_{\rm A}$ is the outer scale on which the fast mode cascade begins, and $l_{\rm p} \sim (l_{\rm A} l_{\rm cut})^{1/2}$ is the characteristic wavelength for wave-particle interactions. For transit time damping and an outer scale of $l_{\rm A}$, we have $l_{\rm cut} \sim (m_{\rm e}/m_{\rm p}) l_{\rm A} (c_{\rm s}/\varv_{\rm A})^{4}$. We thus have $\tau_{\rm w}/\tau_{\rm p} \sim \cp{4\,}(c_{\rm s}/c)(l_{\rm A}/l_{\rm cut})^{1/2} \sim \cp{4\,}(c_{\rm s}/c) (m_{\rm p}/m_{\rm e})^{1/2} \beta^{-1}$. More careful consideration of dimensionless factors boosts this estimate by an order of magnitude to give equation (\ref{eqn:ratios_TTD}).

@@

It is also worth exploring the effect of Burgers' turbulence (weak shocks). \cp{Burgers' turbulence is distinct from other forms of turbulence in that it violates locality in $k$-space--i.e., power does not gradually cascade, but instead can directly jump from large to small scales via a network of weak shocks. Since the Fourier transform of a step function goes as $k^{-1}$, Burgers turbulence has a power spectrum of $P(k) \propto k^{-2}$.} From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), we find: 
\begin{equation}
\frac{D_{pp}^{\rm Burgers}}{D_{pp}^{\rm MHD}} = \left( \frac{\beta}{X_{\rm tu} A} \right)^{1/2} = 0.15 \left( \frac{\beta}{50} \right)^{1/2} \left( \frac{X_{\rm tu}}{0.2} \right)^{-1/2} 
\end{equation}
where we have set $\langle k \rangle_{\mathcal{W}} \approx k_L$ for Burgers' turbulence, i.e. all power is at large scales. This weighting towards larger scales implies a much lower wave-particle interaction rate and thus a diffusion coefficient which is smaller than standard TTD on thermal particles by an order of magnitude. Since $\langle k \rangle_{\mathcal{W}} \approx k_L$ is independent of the cutoff scale $k_{\rm cut}$, this conclusion is unchanged if plasma instabilities regulate the thermal particle mean free path and TTD operates on relativistic particles instead. Since standard TTD on thermal particles was already potentially problematic (equation \ref{eqn:ratios_TTD}), we conclude, in agreement with other assessments \citep{miniati15,brunetti16_review}, that if Burgers turbulence dominates, then turbulent reacceleration will be ineffective\footnote{Note also that since there is no real cascade in Burgers' turbulence, but direct transfer of power from large to small scales, the dissipation time is potentially short. In this case, $\tau_{\rm cl} \sim \tau_{\rm drive}$, the driving time, rather than the turbulent dissipation time.}.

>>>>

We adopt a Kraichnan spectrum ($s=3/2$) for the fast modes, as seen in simulations \citep{cho03}. This can also be written as: 
\begin{equation}
  \label{eq:Wk}
  \mathcal{W}(k) =
\sqrt{2/7\,I_L\,\rho\,\langle \Vph \rangle}\,k^{-3/2},
\end{equation}
where $I_L$ is the volumetric injection rate of turbulence at scale $L$ (which
is assumed to be constant), $\varv_{\rm ph}\approx c_{\rm s}$ is the phase speed
of waves. \cp{Since the Kraichnan spectrum is critical in what follows, it is
  worthwhile taking a moment to recount the origin of the spectral slope $s$ and
  the cascade rate. In the magnetically dominated regime, two counterpropagating
  wave packets of scale $l$ interact on a wave crossing time $\tau_{\rm
    ph}=l/\varv_{\rm ph}$, rather than the eddy turnover time $\tau_{\rm edd} =
  l/\varv_{\rm l}$.  Since $\tau_{\rm ph} \ll \tau_{\rm edd}$, each interaction
  results in a small velocity change $\delta \varv_{\rm l} \sim \varv_{\rm l}
  (\tau_{\rm ph}/\tau_{\rm edd})$. If these changes behave like a random walk,
  the cascade time $\tau_{\rm l}$ it takes for an eddy to become non-linear
  ($\Delta \varv \sim \varv_{\rm l})$ and cascades to smaller scales occurs with
  a characteristic velocity $\varv_{\rm l} \sim \delta \varv_{\rm l} (\tau_{\rm
    l}/\tau_{\rm ph})^{1/2} \sim \varv_{\rm l} (\tau_{\rm ph}/\tau_{\rm edd})\,
  (\tau_{\rm l}/\tau_{\rm ph})^{1/2}$, which we can solve to obtain the cascade
  time:
\begin{equation}
  \label{eqn:tau_l}
\tau_{\rm l} \sim \left(\frac{\tau_{\rm edd}}{\tau_{\rm ph}}\right)^{2} \tau_{\rm ph} \sim \frac{l \varv_{\rm ph}}{\varv_{\rm l}^{2}} 
\end{equation}
where we have implicitly assumed isotropy. This implies a dissipation rate $\epsilon \sim \varv_{\rm l}^{2}/\tau_{\rm l} \sim \varv_{\rm l}^{4}/(l \varv_{\rm ph})$, or $\varv_{\rm l} \sim (\epsilon l \varv_{\rm ph})^{1/4}$. Thus, since $k E(k)\sim \varv_{\rm l}^{2}$, this gives a kinetic energy spectrum: 
\begin{equation}
E(k) \sim (\epsilon \varv_{\rm ph})^{1/2} k^{-3/2}.
\end{equation}}

It is important to realise that this Kraichnan scaling only applies at small scales, where turbulence is magneto-hydrodynamical. At large scales, turbulent motions are subsonic (${\mathcal M}_{\rm s} \sim 0.2-0.5$) but super-Alfv{\'e}nic (${\mathcal M}_{\rm A} \sim 5$). Thus, except in the case where motions are transsonic and weak shocks become important, motions are fundamentally hydrodynamic and turbulence follows a Kolmogorov ($s=5/3$) spectrum. However, while the turbulent energy density $\eps_{\rm turb} \propto l^{2/3}$ decreases at small scales, the magnetic energy density is scale-independent. Thus, at some scale $l_{\rm A} \sim l_L {\mathcal M}_{\rm A}^{-3}$, where $\eps_{\rm turb} \sim \eps_{B}$, the magnetic field becomes dynamically important, and turbulence transitions to the MHD regime. The cutoff scale in equation (\ref{eqn:Wk}) can be computed by setting the turbulent cascade rate for fast modes to the transit time damping rate on thermal electrons. This yields \citep{brunetti07,miniati15}:
\begin{equation}
k_{\rm cut} \approx A k_{\rmn{outer}} \frac{\langle (\delta \varv_{\rmn{outer}})^{2}\rangle^{2}}{c_{\rm s}^{4}}
\label{eqn:k_c1} 
\end{equation}
where $A \approx 11 000$. \cp{If there is an unimpeded cascade from the injection to the cutoff scale, $k_{\rmn{outer}}=k_L$ and $\varv_{\rmn{outer}}=\varv_{\rmn{c}}$. However, in our case the hydrodynamic (Kolmogorov) cascade transitions to the MHD cascade at the Alfv{\'e}n scale so that $k_{\rmn{outer}}=k_{\rmn{A}}$ and $\varv_{\rmn{outer}}=\varv_{\rmn{A}}$ and hence, we get\footnote{\cp{Note that this differs from previous work, which assumes Kraichnan turbulence from the injection scale onward and effectively adopts wave number and compressible velocity at the outer scale $L$ for this estimate of $k_{\rm cut}$.}}
\begin{equation}
k_{\rm cut} \approx A k_{\rmn{A}} \beta^{-2}\,.
\label{eqn:k_c} 
\end{equation}
}
This gives $2\upi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
effective mean free path for CRs, unless plasma instabilities can
mediate interactions between turbulence and particles on smaller
scales \citep{brunetti11}, a possibility we discuss in \S\ref{sect:self-limiting}. Another possibility is that compressible modes dissipate in weak shocks, resulting in Burgers' turbulence $s=2$ \citep{kowal10,porter15,miniati15}. If Burgers turbulence dominates, then particle acceleration rates are too slow in the face of cooling processes to explain radio haloes \citep{miniati15}, and an alternative model for radio haloes is required.

@@

The important effects are best summarised in terms of the acceleration \cp{rate
  which is goverend by advection in momentum space:
\begin{equation}
  \tau_{\rm D}^{-1}\equiv \Gamma_{\rm D}\equiv
  \frac{\dot{p}}{p}=p^{-3}\frac{\partial}{\partial p}\left(p^2D_{pp}\right)
  =\frac{4 D_{pp}}{p^{2}}.
\end{equation}
In the last step we have used that $D_{pp}\propto p^2$ for turbulent
reacceleration (equation \ref{eqn:Dpp}). Hence the acceleration time is independent of momentum.}
%\begin{equation}
%\tau_{\rm D}= \frac{p^{2}}{4 D_{pp}}
%\end{equation}
%which is momentum independent.
This should be compared against the lifetime of turbulence, $\tau_{\rm cl}$, and the cooling time $\tau_{\rm cool}$. In Table~\ref{tab:timescales}, we show both the thermal quantities and the
timescales for CR cooling and (re)acceleration for three different
spatial regions of the RH. The densities \citep{1992A&A...259L..31B} and temperatures \citep{2009ApJ...696.1886B,2001A&A...365L..67A} are derived from X-ray observations. To calculate synchrotron cooling times, we use $B$-fields derived from Faraday rotation measurements \citep{bonafede10}. To calculate the acceleration time, we need to assume an outer scale. We assume an injection scale $k_L=2\upi/\lambda_L$, where $\lambda_L = 100$ kpc, which were assumptions adopted in previous work \citep{2006MNRAS.366.1437S,brunetti07, brunetti11}. This length scale corresponds to an eddy turnover time on the outer scale of \cp{$2\upi\lambda_L\varv_L^{-1} \sim 1.2$~Gyr} if $\varv_L \sim 500 {\rm km \, s^{-1}}$, as is characteristic of a merger. Note that hydrodynamical simulations of clusters have sometimes found larger $\lambda_L$, in some cases comparable to the size of the cluster \citep{vazza11,miniati15}. This choice is degenerate with $X_{\rm tu}$; in \S\ref{sect:self-limiting} we argue that $k_{\rm A}$ is a more appropriate choice, but also find that when the decay time is appropriately scaled, we are relatively insensitive to the choice of $k_L$. We present $\tau_{\rm D}$ for 3 different models, which we discuss in the next section. The reacceleration timescale
$\tau_{\rm D}$ is similar between our three models, where the
difference comes from turbulent profile parametrized with
$\alpha_\rmn{tu}$. This implies that even small differences in the
turbulent profile could impact the seed CRs significantly. Finally, we adopt an duration of acceleration $\tau_{\rm cl} = 650$ Myr, in line with previous assumptions \citep{brunetti07}, roughly corresponding to the turbulent decay time. 
\begin{table}
  \caption{Thermal quantities and timescales for different spatial
    regions in a Coma like cluster.}
\begin{tabular}{l c  c c}
\hline
\hline
& & spatial regions & \\
 & $0.1\,\RH^{(2)}$ & $0.3\,\RH^{(2)}$ & $\RH^{(2)}$   \\
\hline
thermal quantities$^{(1)}$ & & & \\
$\rho$ [$10^{-27}$ g cm$^{-3}$] & 3.0 & 1.6 & 0.15 \\
$T$ [$10^{8}$ K] & 1.4 & 1.0 & 0.58 \\
\hline
timescales$^{(1)}$ & & & \\
$\tau_\rmn{D}$(\Mprimary)$^{(3)}$ [Gyr] & 0.45 & 0.44 & 0.39 \\
$\tau_\rmn{D}$(\Mstream)$^{(3)}$  [Gyr] & 0.50 & 0.47 & 0.34 \\
$\tau_\rmn{D}$(\Mflatturb)$^{(3)}$  [Gyr] & 0.69 & 0.56 & 0.27 \\
$\tau_\rmn{IC/sync}(P=10^4\,m_{\rmn{e}}c)^{(4)}$ [Gyr] & 0.11 & 0.15 & 0.22 \\
$\tau_\rmn{had}(P=100\,m_{\rmn{p}}c)^{(5)}$ [Gyr] & 2.4 & 4.5 & 47 \\
$\tau_\rmn{Coul}(P=\,m_{\rmn{e}}c)^{(6)}$  [Gyr] & 0.0092 & 0.017 & 0.17 \\
\hline
\end{tabular}
\begin{quote}
 Notes: \\ 
 (1) Median quantities from our simulated post-merging cluster g72a derived 
 during last 300~Myrs in time. \\
 (2) Radius of the giant radio halo in Coma where $\RH\approx0.6\,R_{200}$.\\
 (3) Fermi-II reacceleration for both electrons and protons at all energies.\\
 (4) Inverse Compton and synchrotron cooling for electrons.\\
 (5) Catastrophic losses for protons.\\
 (6) Coulomb cooling for electrons (protons factor $m_{\rmn{e}}/m_{\rmn{p}}$ smaller).\\
 \label{tab:timescales}
  \end{quote}
\end{table}

@@

Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$, with velocity $\varv_{\rm A}$. The turbulent reacceleration time is: 
%\begin{equation}
%\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = C_{\rm D} A^{1/2} c k_{\rm A} \frac{\varv_{\rm A}^{2}}{c_{\rm S}^{2}}
%\label{eqn:tau_D} 
%\end{equation}
\cp{
  \begin{equation}
\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = \frac{C_{\rm D}}{A^{1/2}}\, \frac{c}{k_{\rm A}}\, \frac{c_{\rm s}^{2}}{\varv_{\rm A}^{4}}
\label{eqn:tau_D} 
\end{equation}
}
where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equation (\ref{eqn:k_c}). The turbulent decay time is given by the cascade time of fast modes \cp{at the Alfv\'en scale $k=k_{\rmn{A}}$} (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:tau_l}): 
\begin{equation}
  \tau_{\rm decay} = \cp{\frac{\varv_{\rm ph}}{\varv_k^{2} k} = }
  \frac{c_{\rm s}}{\varv_{\rm A}^{2} k_{\rm A}^{}}\,.
\label{eqn:tau_decay} 
\end{equation}
This can be related to the eddy turnover time at the outer scale $\tau_{\rm edd}$ from $l_{\rm A} = L \mathcal{M}_{\rm A}^{-3}$ to: 
\begin{equation}
\tau_{\rm decay} =\frac{L}{\varv_{\rm c}} \left(\frac{c_{\rm s}}{\varv_{\rm c}} \right)^{2} \frac{\varv_{\rm A}}{c_{\rm s}} = 0.7 \, \tau_{\rm edd} \left(\frac{\tilde{X}_{\rm tu}}{0.2}\right)^{-1}  \left(\frac{\beta}{100} \right)^{-1/2}
\end{equation}
\cp{[I get 0.08 as prefactor mainly because of the $2\upi$ conversion from $k$ to $L$.]}
where we have used $\tilde{X}_{\rm tu} \approx (\varv_{\rm c}/c_{\rm s})^{2}$ and $c_{\rm s}/\varv_{\rm A} = \beta^{1/2}$. From equations (\ref{eqn:tau_D}) and (\ref{eqn:tau_decay}), we obtain:
\begin{equation}
  \frac{\tau_{\rm cl}}{\tau_{\rm D}} \approx \frac{\tau_{\rm decay}}{\tau_{\rm D}}
  \cp{= \frac{A^{1/2}}{C_{\rmn{D}}}\,\frac{c_{\rm s}}{c}\,\beta^{-1}}
  = 0.1 \left( \frac{c_{\rm s}}{1500 \, {\rm km \, s^{-1}}} \right) \left( \frac{\beta}{50} \right)^{-1}\,. 
\label{eqn:ratios_TTD} 
\end{equation}
Remarkably, this expression is independent of properties of the turbulence such as $\varv_{\rm c}$, $L$, or $l_{\rm A}$, and depends only on properties of the plasma ($c_{\rm s},\beta$). Ultimately, this arises because the timescale on which a fast mode wave transfers energy due to wave particle interactions in second order Fermi acceleration, $\tau_{\rm p} \sim [\cp{4\,} k_{\rm p} c (\varv_{\rm c}/c)^{2} ]^{-1}$, is closely related to the timescale on which it cascades due to wave-wave interactions, $\tau_{\rm w} \sim c_{\rm s}/(k_{\rm w} \varv_{\rm c}^{2})$. This implies $\tau_{\rm w}/\tau_{\rm p} \sim \cp{4\,} (c_{\rm s}/c)(l_{\rm w}/l_{\rm p})$, where $l_{\rm w} \sim l_{\rm A}$ is the outer scale on which the fast mode cascade begins, and $l_{\rm p} \sim (l_{\rm A} l_{\rm cut})^{1/2}$ is the characteristic wavelength for wave-particle interactions. For transit time damping and an outer scale of $l_{\rm A}$, we have $l_{\rm cut} \sim (m_{\rm e}/m_{\rm p}) l_{\rm A} (c_{\rm s}/\varv_{\rm A})^{4}$. We thus have $\tau_{\rm w}/\tau_{\rm p} \sim \cp{4\,}(c_{\rm s}/c)(l_{\rm A}/l_{\rm cut})^{1/2} \sim \cp{4\,}(c_{\rm s}/c) (m_{\rm p}/m_{\rm e})^{1/2} \beta^{-1}$. More careful consideration of dimensionless factors boosts this estimate by an order of magnitude to give equation (\ref{eqn:ratios_TTD}).

@@

It is also worth exploring the effect of Burgers' turbulence (weak shocks). \cp{Burgers' turbulence is distinct from other forms of turbulence in that it violates locality in $k$-space--i.e., power does not gradually cascade, but instead can directly jump from large to small scales via a network of weak shocks. This implies a short dissipation time and we have in this case, $\tau_{\rm cl} \sim \tau_{\rm drive}$, the driving time, rather than the turbulent dissipation time. Since the Fourier transform of a step function goes as $k^{-1}$, Burgers turbulence has a power spectrum of $P(k) \propto k^{-2}$.} From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), we find: 
\begin{equation}
\frac{D_{pp}^{\rm Burgers}}{D_{pp}^{\rm MHD}} = \left( \frac{\beta}{X_{\rm tu} A} \right)^{1/2} = 0.15 \left( \frac{\beta}{50} \right)^{1/2} \left( \frac{X_{\rm tu}}{0.2} \right)^{-1/2} 
\end{equation}
where we have set $\langle k \rangle_{\mathcal{W}} \approx k_L$ for Burgers' turbulence, i.e. all power is at large scales. This weighting towards larger scales implies a much lower wave-particle interaction rate and thus a diffusion coefficient which is smaller than standard TTD on thermal particles by an order of magnitude. Since $\langle k \rangle_{\mathcal{W}} \approx k_L$ is independent of the cutoff scale $k_{\rm cut}$, this conclusion is unchanged if plasma instabilities regulate the thermal particle mean free path and TTD operates on relativistic particles instead. Since standard TTD on thermal particles was already potentially problematic (equation \ref{eqn:ratios_TTD}), we conclude, in agreement with other assessments \citep{miniati15,brunetti16_review}, that if Burgers turbulence dominates, then turbulent reacceleration will be ineffective.
